---
title: "Package Development"
author: "Armin Rauschenberger"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initialisation

```{r,eval=FALSE}
rm(list=ls(all.names=TRUE))
#install.packages(c("roxygen2","pkgdown","rcmdcheck","usethis","remotes","testthat","devtools","goodpractice","checkglobals","roxylint"))
setwd("C:/Users/arauschenberger/Desktop/corila/package")
```

# Set-up

```{r}
#usethis::use_github_action("check-standard")
#usethis::use_github_action("lint")
#usethis::use_spell_check(lang = "en-GB")
```

# Checks

```{r}
devtools::check()
roxygen2::roxygenise()
rcmdcheck::rcmdcheck()
goodpractice::gp()

devtools::spell_check()
checkglobals::checkglobals(pkg=".")

pkgdown::check_pkgdown()
lintr::lint_package()

#devtools::build()
#devtools::submit_cran()
#pkgdown::build_site()
```

# Setting up a private GitLab mirror of a private GitHub repository:

- Generate fine-grained personal access token (PAT) in GitHub developer settings (repository access: specific repository; repository permissions: read-access to content, i.e., code and metadata).

- Configure private pull mirror in GitLab repository settings (<https://github.com/username/repository.git>, indicating the GitHub username and the GitHub PAT as a password).
