---
title: "Package Development"
author: "Armin Rauschenberger"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initialisation

```{r,eval=FALSE}
rm(list=ls(all.names=TRUE))
#install.packages(c("roxygen2","pkgdown","rcmdcheck","usethis","remotes","testthat","devtools","goodpractice","checkglobals","roxylint", "cyclocomp"))
#remotes::install_github(c("ropensci-review-tools/pkgcheck","ropensci-review-tools/autotest","ropensci-review-tools/srr"))
setwd("C:/Users/arauschenberger/Desktop/corila/package")
```

# Set-up

```{r}
#usethis::use_github_action("check-standard")
#usethis::use_github_action("lint")
#usethis::use_spell_check(lang = "en-GB")
```

# Checks

```{r}
devtools::check()
roxygen2::roxygenise()
rcmdcheck::rcmdcheck()

devtools::spell_check()
checkglobals::checkglobals(pkg=".")

pkgdown::check_pkgdown()
lintr::lint_package()
x <- cyclocomp::cyclocomp_package_dir()

#devtools::build()
#devtools::submit_cran()
#pkgdown::build_site()

# checks for rOpenSci

checks <- setdiff(goodpractice::all_checks(), c("covr", "cyclocomp"))
checks <- checks[!grepl(pattern="rcmdcheck_", x = checks)]
x <- goodpractice::gp(checks = checks)

pkgcheck::pkgcheck(goodpractice=FALSE)
notes <- autotest::autotest_package(exclude=c(".backscale",".forescale",".folds"),test=TRUE)
notes <- autotest::autotest_package(test=TRUE)
srr::srr_stats_roxygen(category = c("ml", "regression"))
```

# Setting up a private GitLab mirror of a private GitHub repository:

- Generate fine-grained personal access token (PAT) in GitHub developer settings (repository access: specific repository; repository permissions: read-access to content, i.e., code and metadata).

- Configure private pull mirror in GitLab repository settings (<https://github.com/username/repository.git>, indicating the GitHub username and the GitHub PAT as a password).
